\labday{Thursday, 1 November 2018}

RF Linear Accelerators (archived Cockcroft Lectures). Lectures 6-8\\


\labday{Friday, 2 November 2018}

Review of beam dynamics


\labday{Monday, 5 November 2018}

Second Lecture on \textit{Introduction to Accelerators} and second half of the \textit{EM \& Relativity}


\labday{Tuesday, 6 November 2018}

One Slide One Minute for CAS\\
Got Max-IV Elegant code to run. Replace $\backslash$ from windows paths for / and change \verb|../| for \verb|./|\\ 
Energy Phase equations.\\
Started reading on FELs and compton sources.

\labday{Wednesday, 7 November 2018}

Outreach training 10-12 \textit{tactile collider}.\\
Look after your mate workshop 13.30-16\\

\labday{Thursday, 8 November 2018}

Inverse compton light sources

\labday{Friday, 9 November 2018}

Elegant \& \verb|vim|

\labday{Monday, 26 November 2018}

Lectures on Magnets and outreach

\labday{Tuesday, 27 November 2018}

Outline of presentation about CAS.

Meeting with Pete

Back to Max IV BC work.\\
Investigate properties of BC1: Layout, Dispersion, $\beta, R_{n6}, T_{n66},$ chromatic amplitude functions and chromatic derivative of dispersion. \textbf{with Elegant}\\
Do it again \textbf{with MAD8dl}\\
Explain the term \textit{Apochromatic} and why it is different to \textit{Achromatic}\\
In the \textit{"How to double..."} CEBAF arcs paper. Recreate Fig. 5 for MAX IV BC's \textbf{with Elegant}.\\
Then equivalent of Norwegian Fig.3 ...\\

\labday{Wednesday, 28 November 2018}
Worked on layout ploting of MAX IV BC1\\
Plots of Dispersion, $\beta, R_{n6}, T_{n66}$\\

\labday{Thursday, 29 November 2018}
Installed MAD8dl\\

\labday{Friday, 30 November 2018}
Plotting beta, R,T for BC1 in Max-IV\\
Prep. Presentation about CAS\\
